---
<<<<<<< HEAD
title: "Regression_Linear"
---

=======
title: "Regression_Linear for africa energy data"
---



>>>>>>> cf13c2484631150564c08cdf77d5417048848c98
---
author: "GARBA Moussa"
date: "2/7/2021"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



<<<<<<< HEAD
```{r }
remove.packages(c("caret"))

```
```{r }
install.packages("caret")
install.packages("ggplot2")
install.packages("lattice")
install.packages("lava")
install.packages("ggforce")

=======

```{r }
install.packages("caret",repos = "http://cran.us.r-project.org")
install.packages("ggplot2",repos = "http://cran.us.r-project.org")
install.packages("lattice",repos = "http://cran.us.r-project.org")
install.packages("lava",repos = "http://cran.us.r-project.org")
install.packages("ggforce",repos = "http://cran.us.r-project.org")
install.packages("mnormt",repos = "http://cran.us.r-project.org")
install.packages("QuantPsyc", repos = "https://cran.rstudio.com/bin/windows/contrib/3.4/mnormt_1.5-5.zip")

install.packages("relaimpo",repos = "http://cran.us.r-project.org")
install.packages("rapportools",repos = "http://cran.us.r-project.org")

install.packages("lm.beta",repos = "http://cran.us.r-project.org")
install.packages("lmtest",repos = "http://cran.us.r-project.org")
install.packages("caTools",repos = "http://cran.us.r-project.org")
install.packages("unmarked",repos = "http://cran.us.r-project.org")

install.packages("lmSupport",repos = "http://cran.us.r-project.org")
>>>>>>> cf13c2484631150564c08cdf77d5417048848c98
```

```{r }
library(tidyverse)
library(readr)
library(data.table)
library(DataExplorer)

library(tidyr)
library(broom)

library(stringr)
library(lubridate)
library(ggforce)
library(reshape2)

library(corrplot)
library(ggplot2)
library(lattice)
library(lava)
library(caret)
<<<<<<< HEAD


=======
library(MASS)
library(rapportools)
library(caTools)
library(unmarked)
library(lm.beta)
library(lmtest)
library(DAAG)
library(relaimpo)
library(lmSupport)
>>>>>>> cf13c2484631150564c08cdf77d5417048848c98

```
# Regression linéaire 


```{r }
#data <-  read.table("/Users/garbamoussa/Desktop/Bureau/R/Regressions_energy_data/Data_source/Data.csv", header=TRUE, sep=";",  comment.char="#",  na.strings="NA", stringsAsFactors=FALSE, quote="", fill=FALSE)

#data <- read_csv("/Users/garbamoussa/Desktop/Bureau/R/Regressions_energy_data/Data_source/Data.csv", col_names = "TRUE",locale = default_locale(), quote = ";", na =c("", "NA"))


#data1 <-  read.table("/Users/garbamoussa/Desktop/Bureau/R/Regressions_energy_data/Data_source/Data1.csv", header=TRUE,sep=";", comment.char="#", na.strings=".", stringsAsFactors=FALSE) 

#data <- read.table("/Users/garbamoussa/Desktop/Bureau/R/Regressions_energy_data/Data_source/Data.csv", header=TRUE, sep=";", quote="\\", fill=TRUE)
```


```{r }
#x = readLines('/Users/garbamoussa/Desktop/Bureau/R/Regressions_energy_data/Data_source/Data.csv')
#y = gsub('","', "','", x) # replace double quotes for each field
#y = gsub('^"|"$', "'", y) # replace trailing and leading double quotes
#z = paste(y, collapse='\n') # turn it back into a table for fread to read
#df = fread(z, quote="'")
#df


```

```{r }


#data<- fread("/Users/garbamoussa/Desktop/Bureau/R/Regressions_energy_data/Data_source/Data.csv",  header = TRUE, sep = ";",quote = "")


#data<-  read.csv("/Users/garbamoussa/Desktop/Bureau/R/Regressions_energy_data/Data_source/Data.csv",header = TRUE, sep = ";" ,row.names = NULL, comment.char = "",stringsAsFactors = FALSE, colClasses= "character", encoding="utf-8", quote = "")


#data <- fread('/Users/garbamoussa/Desktop/Bureau/R/Regressions_energy_data/Data_source/Data.csv', cmd="sed s/","/','/g;s/^"|"$/'/g /Users/garbamoussa/Desktop/Bureau/R/Regressions_energy_data/Data_source/Data.csv")

## les premières importation attribuent "" à certaines colonnes 
data <- read_csv2("/Users/garbamoussa/Desktop/Bureau/R/Regression_with_R/Data_source/Data.csv",locale=locale("sv",encoding="ISO-8859-1"), quote="")

```


```{r }
str(data)

```


```{r }
head(data)
```

```{r }
summary(data)
```


```{r }
data$cn   = as.factor(data$cn)
```


```{r }

```




```{r }
# supprimer la variable dépendante pour le calcul de la multicolnéarité 
df = subset(data, select = -c(Creditex))

# Identifier les variables numériques 
numericData <- df[sapply(df, is.numeric)]

#Calcul de la corrélation 
descrCor <- cor(numericData, use="pairwise.complete.obs")
#descrCor <-  max(descrCor,na.rm=TRUE)
# Afficher la matrice de corrélation
print(descrCor)
```



```{r }
# Visualize Correlation Matrix
corrplot(descrCor, order = "FPC", method="number", type = "lower", tl.cex = 0.7, tl.col = rgb(0, 0, 0))


#corrplot(cor(df), order = "FPC", method = "color", type = "lower", tl.cex = 0.7, tl.col = rgb(0, 0, 0))
```

```{r }


corrplot(descrCor, type="upper", order="hclust", tl.col="black", tl.srt=45)
```

```{r }
# Checking Variables that are highly correlated
highlyCorrelated = findCorrelation(descrCor, cutoff=0.7)

#Identifying Variable Names of Highly Correlated Variables
highlyCorCol = colnames(numericData)[highlyCorrelated]

#Print highly correlated attributes
highlyCorCol


#Remove highly correlated variables and create a new dataset
<<<<<<< HEAD
dat3 = mtcars[, -which(colnames(mtcars) %in% highlyCorCol)]
=======
dat3 = data[, -which(colnames(data) %in% highlyCorCol)]
>>>>>>> cf13c2484631150564c08cdf77d5417048848c98
dim(dat3)



```

```{r }
#Build Linear Regression Model
fit = lm(Creditex ~ ., data=data)

#Check Model Performance
summary(fit)

#Extracting Coefficients
summary(fit)$coeff
anova(fit)

par(mfrow=c(2,2))
plot(fit)
```

```{r }

anova(fit)
```


```{r }

summary(fit)$r.squared
summary(fit)$adj.r.squared
AIC(fit)
BIC(fit)
```


<<<<<<< HEAD
```{r }
=======




```{r }

data<-na.omit(data)
>>>>>>> cf13c2484631150564c08cdf77d5417048848c98
step <- stepAIC(fit, direction="both")
summary(step)


```


```{r }
step <- stepAIC(fit, direction="backward")
summary(step)

```

```{r }
step <- stepAIC(fit, direction="forward")
summary(step)
```


```{r }
#Stepwise Selection with BIC
n = dim(data)[1]
stepBIC = stepAIC(fit,k=log(n))
summary(stepBIC)
```


```{r }
<<<<<<< HEAD

#Autocorrelation Test
durbinWatsonTest(stepBIC)

#Normality Of Residuals (Should be > 0.05)
res=residuals(stepBIC,type="pearson")
shapiro.test(res)
=======
lm.beta(stepBIC)
#Autocorrelation Test
library(car)
durbinWatsonTest(stepBIC)

```

```{r }
#Normality Of Residuals (Should be > 0.05)
res=residuals(stepBIC,type="pearson")
shapiro.test(res)
```


```{r }
>>>>>>> cf13c2484631150564c08cdf77d5417048848c98

#Testing for heteroscedasticity (Should be > 0.05)
ncvTest(stepBIC)

<<<<<<< HEAD
#Outliers – Bonferonni test
outlierTest(stepBIC)

#See Residuals
resid = residuals(stepBIC)

#Relative Importance
install.packages("relaimpo")
library(relaimpo)
=======
```


```{r }
#Outliers – Bonferonni test
outlierTest(stepBIC)

```

```{r }
#See Residuals
resid = residuals(stepBIC)


```





```{r }
#Relative Importance

>>>>>>> cf13c2484631150564c08cdf77d5417048848c98
calc.relimp(stepBIC)

```

<<<<<<< HEAD

```{r }
#Calculating RMSE
rmse = sqrt(mean((dat3$mpg - pred)^2))
print(rmse)

#Calculating Rsquared manually
y = dat3[,c("mpg")]
=======
```{r }

#See Predicted Value
pred = predict(stepBIC,data)
#See Actual vs. Predicted Value
finaldata = cbind(data,pred)
print(head(subset(finaldata, select = c(Creditex,pred))))

```



```{r }
#Calculating RMSE
rmse = sqrt(mean((dat3$Creditex - pred)^2))
print(rmse)

#Calculating Rsquared manually
y = dat3[,c("Creditex")]
>>>>>>> cf13c2484631150564c08cdf77d5417048848c98
R.squared = 1 - sum((y-pred)^2)/sum((y-mean(y))^2)
print(R.squared)

#Calculating Adj. Rsquared manually
n = dim(dat3)[1]
p = dim(summary(stepBIC)$coeff)[1] - 1
adj.r.squared = 1 - (1 - R.squared) * ((n - 1)/(n-p-1))
print(adj.r.squared)

#Box Cox Transformation
<<<<<<< HEAD
library(lmSupport)
modelBoxCox(stepBIC)
```

```{r }
#K-fold cross-validation
library(DAAG)
kfold = cv.lm(data=dat3, stepBIC, m=5)
```

```{r }

```


```{r }

```


```{r }

```


```{r }

```





=======

#modelBoxCox(stepBIC)
```

```{r }
#K-fold cross-validation

#kfold = cv.lm(data=dat3, stepBIC, m=5)
```

>>>>>>> cf13c2484631150564c08cdf77d5417048848c98
